Inferring neural networks from fluorescent calcium imaging using partial correlation and sample weighting

### 2014-05-23 article.tex
empty tabs

\paragraph{Improvement of each stage of our approach\\}
\paragraph{Comparison with other methods\\}

\subsection{Metrics}
\subsection{Data filtering}
\subsection{Signal distribution}
\subsection{ROC AUC results}
\subsection{AUPRC}

>>>>

\paragraph{Improvement of each stage of our approach\\}

\begin{table}[h!]
\begin{tabular}{|c|c||c|c|c|c|c|c|} \hline
\# & Stage & normal-1 & normal-2 & normal-3 & normal-4 & normal-5 & normal-6 \\ \hline
1 & Inverse correlation & & & & &  &  \\ \hline
2 & Pre-processing & & & & &  &  \\ \hline
3 & PCA & & & & &  &  \\ \hline
4 & Weighting & & & & &  &  \\ \hline
5 & Averaging & & & & &  &  \\ \hline

\end{tabular}
\end{table}

Note that we choose the \textit{best} threshold for stages 1 to 4.

\paragraph{Comparison with other methods\\}
\begin{table}[h!]
\begin{tabular}{|c|c||c|c|c|c|c|c|} \hline
\# & Stage & normal-1 & normal-2 & normal-3 & normal-4 & normal-5 & normal-6 \\ \hline
1 & Inverse correlation & & & & &  &  \\ \hline
2 & Correlation & & & & &  &  \\ \hline
3 & GENIE3 & & & & &  &  \\ \hline
4 & GTE & & & & &  &  \\ \hline

\end{tabular}
\end{table}
\subsection{Metrics}
\subsection{Data filtering}
\subsection{Signal distribution}
\subsection{ROC AUC results}
\subsection{AUPRC}
